Debugging by \textit{lastChange}

### 2010-11-04 papers/pldi2011/sigplanconf-template.tex

\authorinfo{Salman Mirghasemi\and Claude Petitpierre}
           {Ecole Polytechnique F\'ed\'erale de Lausanne}
           {\{salman.mirghasemi,claude.petitpierre\}@epfl.ch}

@@

@@

A bug is \textit{reproducible} for a developer when the developer can
start from a determined initial state, operate on the program with a
list of actions, and reproduce the symptoms of the bug. The details of
the execution can change each time we re-execute the buggy program,
but the buggy result is the same.  The reproducibility of the bug
means that the defect is very unlikely to depend on the order of
events during the execution. When the developer selects a value and
asks for \textit{lastChange}, they are expressing the hypothesis that
the value is related to the defect. Therefore the reproducibility of
the bug makes it very unlikely that the \textit{lastChange} will
depend upon order of events during execution.

>>>>

%\authorinfo{Salman Mirghasemi\and Claude Petitpierre}
%           {Ecole Polytechnique F\'ed\'erale de Lausanne}
%           {\{salman.mirghasemi,claude.petitpierre\}@epfl.ch}

\authorinfo{Salman Mirghasemi}
           {Ecole Polytechnique F\'ed\'erale de Lausanne}
           {salman.mirghasemi@epfl.ch}

@@

\authorinfo{Claude Petitpierre}
           {Ecole Polytechnique F\'ed\'erale de Lausanne}
           {claude.petitpierre@epfl.ch}

@@

A bug is \textit{reproducible} for a developer when the developer can
start from a determined initial state, operate on the program with a
list of actions, and reproduce the symptoms of the bug. The details of
the execution can change each time we re-execute the buggy program,
but the buggy result is the same.  The reproducibility of the bug
means that the defect is very unlikely to depend on the order of
events during the execution. When the developer selects a value and
asks for \textit{lastChange}, the developer is expressing the hypothesis that
the value is related to the defect. Therefore the reproducibility of
the bug makes it very unlikely that the \textit{lastChange} will
depend upon order of events during execution.
